%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
\definecolor{awesome}{HTML}{0060a0}
   

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
%\photo[circle,noedge,left]{profile}
\name{Christophe}{Dominik}
\position{Guest scientist}%{\enskip\cdotp\enskip}Security Expert}
\address{Permoserstraße 15 | 04318 Leipzig | Germany}

\mobile{(+49) 176 2758 4402}
\email{christophe.dominik@ufz.de}
%\homepage{www.posquit0.com}
%\github{posquit0}
%\linkedin{posquit0}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
\extrainfo{born 10.11.1985	| 	Married}

%\quote{``Be the change that you want to see in the world. Now!"}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {German Centre for Integrative Biodiversity
Research – iDiv}
  {Deutscher Platz 5e\\04103 Leipzig | Deutschland}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Application for Postdoctoral researcher: Reference file number
157/2018}
% How the letter is opened
\letteropening{Dear  Prof.
Jonathan Chase and Dr. Shane Blowes, Prof. Helmut Hillebrand and Dr. Dorothee Hodapp,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Christophe Dominik~~~·~~~Cover Letter}
  {}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

%\lettersection{About Me}
I would like to express my interest in your postdoctoral research position on the project “Scale-dependent drivers of biodiversity change in marine and terrestrial
ecosystems”. Under the supervision of Pr. Dr. Ralf Seppelt and Dr. Tomáš Václavík at the Helmholtz Centre for Environment Research in Leipzig (Germany), I have recently submitted my PhD thesis and believe that my education and research experience are appropriate for the position. 

%\lettersection{Why Google?}
My research focuses on the role of landscape heterogeneity on the distribution of rice-arthropods in South-East Asia using a classic landscape ecology approach. In my dissertation, I used GIS-software 
and remote sensing data to best describe the landscape heterogeneity and calculated landscape metrics to quantify the landscape composition and configuration. Using multiple statistical methods in R, the findings of my thesis are the first to quantify the effects of the surrounding landscape on rice-arthropods in South-East Asia. The experiences I gained during my PhD allowed me to develop the skills needed to become familiar with landscape ecology, GIS-software, working with a large data-set, and the use of R statistical computing.

%\lettersection{Why Me?}
My research experiences and training have allowed me to gain strong quantitative skills in R. I am well-versed in using multiple statistical methods such as ANOVA, linear mixed models, GLM/GLMM, RLQ and fourth corner analyses (for life-history traits analyses), which helped me answer the research questions asked in my thesis. Additionally, I am also proficient in ArcGIS, mapping land cover/land use, and calculating landscape metrics. Finally, being part of an international scientific project (LEGATO), I established a valuable network that will benefit my future research work. The present offered postdoctoral position would be a great opportunity to pursue my work and expand my research experiences. 

%\lettersection{Why Me?}
I have a strong academic background in landscape ecology, and I believe that I can apply my knowledge and experience to the German Centre for Integrative Biodiversity Research (iDiv) Halle-Jena-Leipzig. My previous experiences are highly relevant for the topic of biodiversity change in both terrestrial and marine ecosystems. Indeed, my academic training (Master) at the University of La Réunion provided me with a strong foundation in tropical marine and terrestrial ecosystems. Additionally, I am greatly interested to focus once again on identifying drivers of biodiversity change (whether in terrestrial or marine ecosystems) as my previous experiences allow me to apply similar methods and approaches. I look forward to working in a research institute that shares the same values and research interests as I do (i.e. identifying patterns of biodiversity, ecosystem services, sustainable land-management) – and I am excited about the further opportunities which may arise from our collaboration.

%\lettersection{Why Me?}
Enclosed is a copy of my CV, which fully details my qualifications for the position. Please let me know if I can provide additional information or materials such as publications to aid you in the evaluation of my candidacy. Thank you for your time and consideration. I look forward to speaking with you about this exciting opportunity. 

\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}
