%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{References}


\begin{cvparagraph}

%---------------------------------------------------------
 \vspace{.5\baselineskip} 

\textbf{Dr. Tomáš VÁCLAVÍK}\\
Department of Ecology \& Environmental Sciences\\
Palacký University Olomouc,  Faculty of Science – 78371 Olomouc, Czech Republic\\
\faEnvelope\hspace{.3\baselineskip}{tomas.vaclavik@upol.cz}\\
\faMobile\hspace{0.7\baselineskip}{(+420) 585 634 555}\\
\\
\textbf{Note}: Dr. Václavík co-supervised my work during my PhD. He has great insight of the work I have accomplished as a PhD student.\\
\\
 \vspace{5\baselineskip} 
 
\textbf{Prof. Dr. Ralf SEPPELT}\\
Department of Computational Landscape Ecology\\
Helmholtz Centre for Environmental Research UFZ – 04318 Leipzig. Germany\\
\faEnvelope\hspace{.3\baselineskip}{ralf.seppelt@ufz.de}\\
\faMobile\hspace{0.7\baselineskip}{(+49) 341 235 1250}\\
\\
\textbf{Note}: Prof. Dr. Seppelt was my main supervisor and gave me the freedom to lead my own research during my PhD.\\
\\
\textbf{Dr. Finbarr G. HORGAN}\\
International Rice Research Institute - DAPO Box 7777, Metro Manila, Philippines\\
Centre for Compassionate Conservation, University of Technology Sydney - Sydney, NSW 2007, Australia\\
\faEnvelope\hspace{.3\baselineskip}{Finbarr.Horgan@uts.edu.au}\\
\\
\textbf{Note}: Dr. Horgan and I worked together during my research in the Philippines. We planned the fieldwork in the mountainous region of the Philippines and are now collaborating on publications.
\\

\end{cvparagraph}


