%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {PhD student/Guest scientist | Supervisors: Pr. Dr. Ralf Seppelt and Dr. Tomáš Václavík} % Job title
    {Helmholtz Centre for Environmental Research (UFZ)} % Organization
    {Leipzig, Germany} % Location
    {Jul. 2012 - Sep. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Research topic: The effects of landscape heterogeneity
on arthropod communities in rice agro-ecosystems.}
        \item {Mapping of 30 study sites using ArcGIS 10.}
         \item {Quantification of landscape heterogeneity via calculation of landscape metrics (Fragstats).}
        \item {Use of multiple linear regression models, linear mixed effects models,  dissimilarity matrices, RLQ method, fourth-corner analyses.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Guest scientist} % Job title
    {International Rice Research Institute (IRRI)} % Organization
    {Los Baños Laguna, Philippines} % Location
    {2013 - 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Sampling of rice-arthropods and identification of arthropods ($\sim$ 80000 individuals) to morphospecies level ($\sim$ 200 species).}
        \item {Experience in networking with local researchers and supervision of field work assistants in the mountainous region of the Philippines.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research assistant} % Job title
    {Centre national de la recherche scientifique (CNRS)} % Organization
    { Nantes, France} % Location
    {Mar. 2012 - Jun. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Research topic: Influence of landscape structures of the salinas on terrestrial bird distribution of the Ré Island (Western France).}
        \item {Bird counts of common European passerine birds in salinas during a two weeks period.}
        \item {Mapping of the salinas located in Ré Island using ArcView 3.1 and calculation of landscape metrics (Fragstats).}
        \item {Multivariate analysis and multiple regressions used to test links between landscape metrics and bird distribution (dissimilarity matrices, hierarchical clustering).}               
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Undergraduate Research student | Supervisor: Dr. Laurent Godet | M.Sc.2 Thesis grade: 16.67/20 Rank: 2/17} % Job title
    {Centre national de la recherche scientifique (CNRS)} % Organization
    {Nantes, France} % Location
    {Feb. 2011 - Jun. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Research topic: Influence of landscape structures of the salinas on terrestrial bird distribution in the Guérande basin (NW France).}
        \item {Material/Methods and analysis similar to research experience in 2012.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Undergraduate Research student | Supervisor: Dr. Serge Quilici | M.Sc.1 Thesis grade: 15.73/20 Rank: 5/35} % Job title
    {CIRAD} % Organization
    {Saint-Pierre, Réunion Island} % Location
    {Jan. 2010 - Jun. 2010} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Research topic: Biology study of the sawfly \textit{Cibdela janthina}: Food specificity and characterization of the different larval instars.}
        \item {Infestation of four plant species within the Rosacea family with 40 larvae of \textit{C.janthina}.}
        \item {Daily survival monitoring and GLM analysis.}
                                             \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
